Understanding Complex Patterns in Social, Geographic, and Economic Inequities in COVID-19 Mortality at the County Level in the US Using Generalized Additive Models

### 2022-12-01 manuscript/manuscript.rmd

Generalized additive models (GAMs) improve upon generalized linear models by
allowing for the fitting of smooth functions that transform right-hand-side variables.
This is a convenient means to account for nonlinear relationships between the
outcome and predictor variables. Whereas a generalized linear model may look like 
$$ g(\mu_i) = \beta_0 + \beta_1 x_{i1} + \beta_2 x_{i2} + \beta_3 x_{i3} ...$$ 
a generalized additive model could look like 
$$ g(\mu_i) = \mathbf A_i \mathbf \theta + f_1(x_{i1}) + f_2(x_{i2}) + f_3(x_{i3}, x_{i4}) + \dots$$
where the expected value of the outcome is given as $\mu_i \equiv \mathbb E(Y_i)$, 
$\mathbf A_i$ is a row of the model matrix 
for any strictly non-parametric model components, $\mathbf \theta$ is the corresponding
parameter vector, and the $f_j$ are smooth functions of the covariates $x_k$ [@wood_generalized_2017].

>>>>

Generalized additive models (GAMs) improve upon generalized linear models by
allowing for the fitting of smooth functions that transform right-hand-side variables.
This is a convenient means to account for nonlinear relationships between the
outcome and predictor variables. Whereas a generalized linear model may look like 
$$ g(\mu_i) = \beta_0 + \beta_1 x_{i1} + \beta_2 x_{i2} + \beta_3 x_{i3} ...$$ 
a generalized additive model could look like 
$$ g(\mu_i) = \mathbf A_i \mathbf \theta + f_1(x_{i1}) + f_2(x_{i2}) + f_3(x_{i3}, x_{i4}) + \dots$$
where the expected value of the outcome is given as $\mu_i \equiv \mathbb E(Y_i)$, 
$\mathbf A_i$ is a row of the model matrix 
for any strictly parametric model components, $\mathbf \theta$ is the corresponding
parameter vector, and the $f_j$ are smooth functions of the covariates $x_k$ [@wood_generalized_2017].
